Project Proposal: The Core Of The Poodle

### 2015-11-01 project/proposal/Project_proposal.tex
mein shit

\section{ The Idea}
Most lifescience labs manage their data for primers and plasmids via excel spreedsheats or other uncomfortable software solutions. Especially when these sheets grow over time the disadvantages of those spreedsheats become clear in aspects of time consuming searches or unorganized entries. 
\\
Our idea is to create an open source tool, which tries to optimize the organization and speed of getting to the desired data.

\section{ The Structure}
General we splitted the project in several modules. First we want to list the basic ones. These are the data base (DB) module, which we want to realise with SQL lite and .csv-files. These should be automatically loaded into the database and also should be automatically exported.
The next most important module is the GUI which should give the user the possibility of intuitive usage of the DB. Also we want to restrict the user to a minimum of needed rules, when for example making new entries, to verify a clear structured DB.\\
Following now the applications, which should run on the server and provide some useful functions.\\
The integration of the BLAST or DIAMOND search algorithm. This is useful for designing new Arrays or modifying plasmids, because it's is wanted to do the changes in the least amount of steps, which is of only possible if the most similar sequence is known.\\
Also a alignment tool can be very useful to visualize the found results. For the alignments the Hirschberg algorithm should be used.\\
The last module idea was to integrate information to the data from other DBs. If for example a certain protein or domain is incorporated into a plasmid it is useful to have the PDB reference or even integrated informations of the proteins.
	\begin{figure}[h]
		\includegraphics[scale=0.5]{img/Structure.png}
	\end{figure}

@@

	\begin{figure}[h]
		\includegraphics[scale=0.5]{img/Time.png}
	\end{figure}

>>>>

\section{ The Idea}
Most lifescience labs manage their data for primers and plasmids via excel spreadsheets or other uncomfortable software solutions. Especially when these sheets grow over time the disadvantages of those spreadsheets become clear in aspects of time consuming searches or unorganized entries. 
\\
Our idea is to create an open source tool, which tries to optimize the organization and speed of getting to the desired data.

\section{ The Structure}
General we splitted the project in several modules. First we want to list the basic ones. These are the data base (DB) module, which we want to realise with SQL lite and .csv-files. These should be automatically loaded into the database and also should be automatically exported.
The next most important module is the GUI which should give the user the possibility of intuitive usage of the DB. Also we want to restrict the user to a minimum of needed rules, when for example making new entries, to verify a clear structured DB.\\
Following now the applications, which should run on the server and provide some useful functions.\\
The integration of the BLAST or DIAMOND search algorithm. This is useful for designing new Arrays or modifying plasmids, because it's is wanted to do the changes in the least amount of steps, which is of only possible if the most similar sequence is known.\\
Also a alignment tool can be very useful to visualize the found results. For the alignments the Hirschberg algorithm should be used.\\
The last module idea was to integrate information to the data from other DBs. If for example a certain protein or domain is incorporated into a plasmid it is useful to have the PDB reference or even integrated informations of the proteins.
	\begin{figure}[h]
		\centering
		\includegraphics[width=0.5\textwidth]{img/Structure.png}
	\end{figure}

@@

	\begin{figure}[h]
		\includegraphics[width=\textwidth]{img/Time.png}
	\end{figure}
